### 2019-09-28 conflog.tex
makes updates
adds section about banquet space

The Illini Union is capable of hosting the entire technical program of the ANS Student Conference. This keeps the conference contained in one convenient location while being within easy access of the rest of the campus. Technical sessions will be held in a combination of rooms on the second, third, and fourth floors of The Union. Each of these rooms have at least enough capacity for 42 people, lecture style, and A/V capability. There will also be rooms available to have panels and workshops during the course of the technical program. The Illini Rooms A and B will be a combined space for the career fair while Illini Room C and the south lounge will host the poster sessions. We will keep the space open to allow the poster sessions and career fair to share attendance and encourage networking. A detailed list of room capacities and floor plans are located in Appendix D: Building Layout.

\subsection{Conference Contingency Plan}
In the event that the Union has reduced availability during the conference we have the ability to host technical sessions and workshops at a combination of buildings: The National Center for Supercomputing Applications (NCSA) and Beckman Institute. These two buildings have large capacity rooms and small capacity rooms. As these buildings are UIUC property, the cost of renting them are significantly reduced compared to a private facility. Additionally, these two buildings are adjacent to one another and are at most a 10 minute walk from the Union. See Appendix E for a map marking the locations of the proposed conference facilities.\\

@@

@@

\begin{center}
   \begin{tabular}{lcccc}
   \hline\hline
   \textbf{School}&\textbf{Estimated Mileage (mi)}&\textbf{Driving Time (hrs)}&\textbf{Fuel Cost}&\textbf{Per Person}\\
   \hline\hline
    Purdue University&90&1h 40m&\$21.86&\$5.47\\
    University of Cincinnati&233& 3h 40m&\$56.60&\$14.15\\
    Air Force Tech &250&3h 58m&\$60.73&\$15.18\\
    University of Wisconsin&253&4h&\$61.46&\$15.36\\
    Missouri University S \& T &279&4h 21m&\$67.77&\$16.94\\
    U. Missouri - Columbia&291&4h 28m&\$70.69&\$17.67\\
    Ohio State University&302&4h 47m&\$73.36&\$18.34\\
    University of Michigan&345&5h 17m&\$83.81&\$20.95\\
    Vanderbilt University&373&5h 33m&\$90.61&\$22.65\\
    Iowa State University&378&5h 44m&\$91.82&\$22.96\\
    \hline
    Average&279&4h 22m&\$67.87&\$16.97

    \end{tabular} 
\end{center}

>>>>

The Illini Union is capable of hosting the entire technical program of the ANS Student Conference. This keeps the conference contained in one convenient location while being within easy access of the rest of the campus. Technical sessions will be held in a combination of rooms on the second, third, and fourth floors of The Union. Each of these rooms have at least enough capacity for 42 people, lecture style, and A/V capability. There will also be rooms available to have panels and workshops during the course of the technical program. The Illini Rooms A and B will be a combined space for the career fair while Illini Room C and the south lounge will host the poster sessions. We will keep the space open to allow the poster sessions and career fair to share attendance and encourage networking. A detailed list of room capacities and floor plans are located in Appendix D: Building Layout. \\

\subsection{Banquet Space}
\subsubsection{Garden Hotel in Urbana}
The opening ceremony dinner on Thursday night will be hosted at the Garden Hotel in Urbana. They have a capacity of 600 people in rounds and offer in house catering as well as AV capabilities. This location was chosen for its convenience, as it would be the primary hotel for the conference.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{garden_dinner.jpg}
    \caption{The Garden Hotel Banquet Hall with capacity for 600 people in rounds.}
\end{figure}

\subsubsection{IHotel}
Dinner on Friday night will be hosted at the IHotel. The IHotel is undergoing an expansion that will increase the capacity of their banquet space to 690 people in rounds. This expansion is set to be completed by Fall 2020. We will be hosting a social at the 77 Club in Memorial Stadium, just up the street. Information about the IHotel expansion is included in Appendix D.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\textwidth]{ihotel-dinner.png}
    \caption{The current 400-person banquet space at the IHotel.}
\end{figure}

\subsubsection{Illini Union}
After the career fair is taken down on Saturday the final dinner will be set up in the combined Illini Rooms, which has a seating capacity of 496 people in rounds. Catering will be provided by Universiy Catering which allows us to avoid the 20\% gratuity for services.\\

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{illinirooms.jpg}
    \caption{The combined Illini rooms with capacity for 496 in rounds.}
\end{figure}

\subsection{Conference Contingency Plan}
In the event that the Union has reduced availability during the conference we have the ability to host technical sessions and workshops at a combination of buildings: The National Center for Supercomputing Applications (NCSA) and Beckman Institute. These two buildings have large capacity rooms and small capacity rooms. As these buildings are UIUC property, the cost of renting them are significantly reduced compared to a private facility. Additionally, these two buildings are adjacent to one another and are at most a 10 minute walk from the Union. We could also host all technical sessions at the IHotel. Hosting at the IHotel is more expensive than hosting in University buildings and would also require additional transportation options. We would need to reevaluate some parts of our budget in order to host the technical program at this venue. See Appendix E for a map marking the locations of the proposed conference facilities.\\

@@

\subsection{Dining}
\subsubsection{Breakfast}
Our primary hotel, the Garden Hotel in Urbana, soon to be the Radisson Hotel, serves complimentary breakfast every morning. Due to this, we will not be catering breakfast at the Illini Union during the conference. Guests staying at the Illini Union Hotel are provided with vouchers for breakfast at the food court in the basement of the Union. The food court offers Einstein Brothers, Starbucks, Garbanzo Mediterranean, and more. 
\subsubsection{Lunch}
\subsubsection{Dinner}

\textbf{Thursday Night}\\
\textbf{Friday Night}\\
\textbf{Saturday Night}\\

@@

\begin{center}
   \begin{tabular}{lcccc}
   \hline\hline
   \textbf{School}&\textbf{Estimated Mileage (mi)}&\textbf{Driving Time (hrs)}&\textbf{Fuel Cost*}&\textbf{Per Person**}\\
   \hline\hline
    Purdue University&90&1h 40m&\$21.86&\$5.47\\
    University of Cincinnati&233& 3h 40m&\$56.60&\$14.15\\
    Air Force Tech &250&3h 58m&\$60.73&\$15.18\\
    University of Wisconsin&253&4h&\$61.46&\$15.36\\
    Missouri University S \& T &279&4h 21m&\$67.77&\$16.94\\
    U. Missouri - Columbia&291&4h 28m&\$70.69&\$17.67\\
    Ohio State University&302&4h 47m&\$73.36&\$18.34\\
    University of Michigan&345&5h 17m&\$83.81&\$20.95\\
    Vanderbilt University&373&5h 33m&\$90.61&\$22.65\\
    Iowa State University&378&5h 44m&\$91.82&\$22.96\\
    \hline
    Average&279&4h 22m&\$67.87&\$16.97

    \end{tabular} 
\end{center}
\textbf{*}\textit{Estimated assuming an average 23 MPG}\\
\textbf{**}\textit{Assumes four people in a car}
